Observed vs. Simulated Year Comparison

### 2023-01-26 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_1, "", show_diags = "never")
```

@@

```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_2, "", show_diags = "never")
```

@@

```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_3, "", show_diags = "never")
```

>>>>

---
editor_options: 
  chunk_output_type: console
---

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("^G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_1, ".", show_diags = "never")
```

@@

```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_2, ".", show_diags = "never")
```

@@

```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_3, ".", show_diags = "never")
```

### 2023-01-26 03-post-process/output-plots-children/05-length-based-values.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run

  # summarize scaled egg abundance
  E_scaled_mean = post_summ(post_E, "")["mean",]
  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
  E_scaled_upr = post_summ(post_E, "")["97.5%",]

@@

  # extract summarize predicted length
  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]

@@

  # extract summarize predicted growth
  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]

@@

  # extract summarize predicted length
  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]

@@

  # extract summarize predicted length
  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]

>>>>

  # summarize scaled egg abundance
  E_scaled_mean = post_summ(post_E, ".")["mean",]
  E_scaled_lwr = post_summ(post_E, ".")["2.5%",]
  E_scaled_upr = post_summ(post_E, ".")["97.5%",]

@@

  # extract summarize predicted length
  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]

@@

  # extract summarize predicted growth
  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]

@@

  # extract summarize predicted length
  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]

@@

  # extract summarize predicted length
  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
